%-------------------------
% Resume in Latex
% Author : Bernard Tomczyk
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Bernard Tomczyk} \\ \vspace{1pt}
    \small +XX XXXX XXX XXX $|$ \href{mailto:???}{\underline{XXX@Xmail.com}} $|$ 
    \href{https://linkedin.com/in/???}{\underline{linkedin.com/in/bernardtomczyk}} $|$
    \href{https://github.com/???}{\underline{github.com/bentomczyk}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lancaster University}{Lancaster, UK}
      {Master of Science (MSci) in Computer Science (with Industrial Experience)}{Oct. 2019 -- July 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Predicted}: First Class Honours (75\% Average)}
        \resumeItem{\textbf{Relevant Modules}: Data Structures and Algorithms, Artificial Intelligence, Data Mining, Operating Systems, Networking,
Advanced Networking, Software Development.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {AI Foundry}{\small{\emph{Lancaster, UK}}}
      {AI Engineer (Conveyancing Project)}{\normalsize{Nov. 2022 -- Jan 2023}}
      \resumeItemListStart
        \resumeItem{Worked with a large conveyancing firm to optimize workflow.}
        \resumeItem{Trained and utilised natural language processing models to simplify document analysis.}
      \resumeItemListEnd

    \resumeProjectHeading
        {\emph{AI Engineer (Medical Project)}}{{\normalsize{July 2022 -- Aug. 2022}}}
            \resumeItemListStart
            \resumeItem{Worked with a leading medical firm to prototype AI systems that improve quality of life for patients.}
            \resumeItem{Studied, built and trained convolutional neural network models on a bespoke data-set to recognise and track specialised equipment to determine fluid viscosity.}
            \resumeItem{Collected and labelled custom data-sets for prototyping and training purposes.}
        \resumeItemListEnd

    \resumeSubheading
      {FunTech}{Aug. 2022 -- Sep. 2022}
      {Computer Science Tutor}{London, UK}
      \resumeItemListStart
        \resumeItem{Trained and taught various engaging week-long Computer Science courses to students across many age groups.}
        \resumeItem{Covered topics ranging from Object Oriented Programming principles to building Neural Networks.}
    \resumeItemListEnd

    \resumeSubheading
      {Lancaster University}{Feb. 2022 -- July 2022}
      {Computer Science Ambassador}{Lancaster, UK}
      \resumeItemListStart
        \resumeItem{Gave speeches to hundreds of prospective offer-holders and parents about the course and the Computer Science Society.}
        \resumeItem{Worked with lecturers to provide a welcoming and informative experience for the visitors}
      \resumeItemListEnd

    \resumeSubheading
      {Lancaster University Computer Science Society}{2021 -- 2022}
      {President, Elected}{Lancaster, UK}
    \resumeSubheading
      {Lancaster University Economics Society}{2021 -- 2023}
      {Senior Exec Member, Elected to Committee}{Lancaster, UK}
    

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{YoYo!} $|$ \emph{Unity, C\#, GitHub, GitKraken, Adobe Suite, Blender}}{2018 -- 2021}
          \resumeItemListStart
            \resumeItem{Managed a small development team in an Agile development process to plan, develop and maintain a successful mobile phone game.}
            \resumeItem{Engaged with publishing companies and ad agencies to cultivate over 15k downloads and maintain a 4.9-star rating on the Google Play store and App Store.}
            \resumeItem{Utilised GitHub Repos to manage collaboration.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Dirty Drifters} $|$ \emph{Unity, C\#, GitHub, GitKraken, Blender}}{2020}
          \resumeItemListStart
            \resumeItem{Winner of Audio Mob Game Jam (2020)}
            \resumeItem{Planned and developed a mobile phone game in under one month, creatively implementing a third-party audio advertising concept.}
            \resumeItem{Delivered a working and fun game under tight time constraints, in a small development team.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Evaluating defences against adversarial attacks on NNs} $|$ \emph{Python, Google Colab, PyTorch}}{2023}
          \resumeItemListStart
            \resumeItem{Third year dissertation on adversarial attacks on facial recognition neural networks.}
            \resumeItem{Thoroughly researched convolutional neural networks, computer vision, facial recognition.}
            \resumeItem{Implemented and evaluated the effects of adversarial attacks against neural networks and how to best defend them.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, C\#, Python, C, SQL, HTML/CSS} \\
     \textbf{Tools}{: Git, Docker, Google Colab, VS Code, Visual Studio, PyCharm, Linux, Overleaf} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, PyTorch, TensorFlow, Keras, SciPy}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}